### 2019-02-18 sections/relatedwork.tex
some stuff in intuition
merge all communication paragraphs
process algebras wip

The central objective of processes is to model patterns of their behaviour.
These patterns of behaviour manifest themselves in sequences of actions that processes can engage in.
Actions can be events from the environment, or signals send internally between processes.
Processes are a way to model synchronisation patterns.

@@

%%NOTE: Focus on what TOP is good at --TS
% \CSP has a formal semantics that allows various kinds of correctness proofs, including equality of processes, and adherence to a specification.
% This allows applications in program correctness, proofs of deadlock freedom, liveness, or verification of protocols.
%
% \TOP focuses less on formal correctness, and more on practical applicability.
The big difference between processes and tasks is the intended level of abstraction.
While processes are used to explicitly model low-level details about communication, tasks hide these details and provide high-level communication mechanisms to the programmer.
It wants to be a calculus with intuitive semantics that facilitates communication between programmers and domain experts.
Such programs are supposed to hide implementation details from domain experts while containing enough information to allow automatic generation of executable applications, including user interfaces.

@@

@@

\paragraph{Communication between subsystems}

%
% \CSP's semicolon is like an internal step $t \Then e$ in \TOP where $t$ uses $\Unit$ to signal when it is done, and $e$ never fails.
\CSP uses prefixing for both internal and external communication.
Prefixing becomes internal by using \emph{concealment}.
Processes must take any concealed steps as soon as possible, before any further communication with the environment can take place.
This means concealed actions have priority over exposed ones.
This introduces the possibility of diverging computations, that is processes which continuously take internal steps without ever being able to engage in external communication.

>>>>

There are two main differences between \TOP and process algebras.

The first is a difference in scope.
Process algebras focus on modelling the input/output behaviour of processes, by explicitly stating which actions are sent and received at certain points in the program.
The goal of process algebras is formal reasoning about the interaction between subprocesses.
Typically, one wishes to prove properties such as deadlock-freedom, liveness, or adherence to a protocol specification.

The focus of \TOP is to model collaboration patterns, with the explicit goal of not having to specify how exactly subtasks communicate.
The declarative specification of data dependencies between subtasks enables our system to hide such details.

TODO: continue here

@@

%%NOTE: Focus on what TOP is good at --TS
% \CSP has a formal semantics that allows various kinds of correctness proofs, including equality of processes, and adherence to a specification.
% This allows applications in program correctness, proofs of deadlock freedom, liveness, or verification of protocols.
%
% \TOP focuses less on formal correctness, and more on practical applicability.
The big difference between processes and tasks is the level of detail in which programmers need to specify communication between modules.
While processes are used to explicitly model low-level details about communication, tasks hide these details and provide high-level communication mechanisms to the programmer.
It wants to be a calculus with intuitive semantics that facilitates communication between programmers and domain experts.
Such programs are supposed to hide implementation details from domain experts while containing enough information to allow automatic generation of executable applications, including user interfaces.

@@

% \paragraph{Communication with the environment}

@@

% \paragraph{Communication between subsystems}

% \CSP's semicolon is like an internal step $t \Then e$ in \TOP where $t$ uses $\Unit$ to signal when it is done, and $e$ never fails.
\CSP uses prefixing for both internal and external communication.
Prefixing becomes internal by using \emph{concealment}.
Processes must take any concealed steps as soon as possible, before any further communication with the environment can take place.
This means concealed actions have priority over exposed ones.
This introduces the possibility of diverging computations, that is processes which continuously take internal steps without ever being able to engage in external communication.
